Accelerating Deep Neural Network Training on FPGAs Facilitating the Use of Variable Precision

### 2018-06-25 SWoPP2018 Paper/paper.tex
Added email for Matsuoka-sensei.
Lines for FPGA intro.

\author{Erwin de Haan}{TiTech,TUDelft}[e.r.dehaan@student.tudelft.nl]
\author{Arthur Podobas}{TiTech}[podobas.a.aa@m.titech.ac.jp]
\author{Satoshi Matsuoka}{TiTech}

@@

\section{A FPGA-based CNN Framework}
\subsection{Field-Programmable Gate-Arrays}
Small intro to FPGAs.

>>>>

\author{Erwin de Haan}{TiTech,TUDelft}[e.r.dehaan@student.tudelft.nl]
\author{Arthur Podobas}{TiTech}[podobas.a.aa@m.titech.ac.jp]
\author{Satoshi Matsuoka}{TiTech}[matsu@is.titech.ac.jp]

@@

\section{A FPGA-based CNN Framework}
\subsection{Field-Programmable Gate-Arrays}
%Small intro to FPGAs.
FPGAs can be used for a great variety of things, from accelerating computational algorithms to implementating a hardware design before taping out full chip.
They are devices that can represent reconfigurable hardware. 
The fabric they are made up of consists of vast arrays of switches and other routing hardware to connect all the functional elements, like multipliers, block RAM and look up tables, in any way possible.
This makes them very suitable for the research described in this paper.
It gives total freedom to design a hardware implementation to explore algorithms in a hardware setting.
